Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
image noise figure

>>>>

\begin{figure}
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=3.0in}
  \caption{\label{fig:image_noise} Illustration of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical color stretches.}
 \end{center}
\end{figure}
